Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-02-19 supplementary_material.tex
Updates from Overleaf

In addition to section~7.1, we provide more detailed comparisons with GLAD-M15. Fig.~\ref{fig:m15_hotspot} shows the comparisons of $V_{sv}$ perturbations in the plumes and Fig.~\ref{fig:m15_subudction} shows comparisons n the subduction areas. In both comparison figures, GLAD-M25 shows significant enhancement and emerging features compared to GLAD-M15.

>>>>

In addition to section~7.1, we provide more detailed comparisons with GLAD-M15. Fig.~\ref{fig:m15_hotspot} shows the comparisons of $V_{sv}$ perturbations in the plumes and Fig.~\ref{fig:m15_subduction} shows comparisons n the subduction areas. In both figures, GLAD-M25 shows enhancements and emerging features compared to GLAD-M15.
